Timing and magnitude of climate driven range shifts in transboundary fish stocks challenge their management

### 2021-11-24 Scripts/Manuscript.Rmd
Misc

**Shifts in the SSR of the top 5 most valuable transboundary stocks of each country are projected to be 65 $\pm$ 21% by 2030 and 78 $\pm$ 18% by 2050 in 77% of the world's EEZs (Figure SX). In some cases, the SSR of one EEZ is projected to increase more than double relative to their neighbors (e.g., from 10% to 30% SSR). Some of these EEZs include Guatemala gaining from Mexico in the Pacific, Mozambique from Madagascar, and Russia from Norway and Japan in the Barents Sea**

>>>>

**Shifts in the SSR of the top 5 most valuable transboundary stocks of each country are projected to be 65 $\pm$ 21% by 2030 and 78 $\pm$ 18% by 2050 in 77% of the world's EEZs (Fig. \@ref(fig:toeFigureS10)). In some cases, the SSR of one EEZ is projected to increase more than double relative to their neighbors (e.g., from 10% to 30% SSR). Some of these EEZs include Guatemala gaining from Mexico in the Pacific, Mozambique from Madagascar, and Russia from Norway and Japan in the Barents Sea**
